---
title: "Obesity and GLP-1s"
format: 
  html:
    fontsize: 11px
    mainfont: "Arial"
---

```{r}
#| label: load-packages
#| include: false

library(dplyr)
library(readr)
library(here)
library(glue)
library(tidyr)
library(stringr)
library(scales) ## format label_number
library(gt) ## gt table
library(ggplot2)
library(fpp2) # Forecasting: Principles and Practice" (2nd Edition)
library(lubridate) # interval
```

```{r}
#| label: import-data
#| include: false

directory_name <- "data"
date_tirzepatide_ng <-as.Date("2024-12-23")
date_tirzepatide_diab <-as.Date("2023-10-25")

label_number_n <- label_number(1, 1, big.mark=",")
label_perc_n <- label_percent(accuracy =.0001)

#### practice level orlistat data
df_orlistat_practice <- read_csv(here::here(directory_name,"orlistat_practice.csv.gz")) 

#### practice level tirzepatide data
df_tirzepatide_practice <- read_csv(here::here(directory_name,"tirzepatide_practice.csv.gz")) 

### practice statistics data
df_practice_stats <- read_csv(here::here(directory_name,"practice_info_full.csv.gz")) ### as far back as 2015

### ccgs info
df_hscic_ccgs <- read_csv(here::here(directory_name,"practice_ccgs.csv.gz")) %>%
  select("code","name","stp_id", "regional_team_id","org_type") 

### region info
df_regions <- read_csv(here::here("data","NHS_England_Names_and_Codes_in_England.csv")) %>%
  rename(regional_team = NHSER24CDH ,region = NHSER24NM) %>%
  dplyr::select(regional_team,region)

```

```{r}
#| label: create-regional-stats
#| include: false

### join region information to the practice stats
df_region_stats <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  left_join(df_regions,by=join_by(regional_team_id ==regional_team )) %>%
  group_by(regional_team_id,month) %>%
  summarise(total_list_size=sum(total_list_size, na.rm = TRUE),
            regional_team_id = last(regional_team_id ),
              region = last(region ))

```

https://cks.nice.org.uk/topics/obesity/prescribing-information/

Important aspects of prescribing information relevant to primary healthcare are covered in this section specifically for the drugs recommended in this CKS topic. For further information on contraindications, cautions, drug interactions, and adverse effects, see the electronic Medicines Compendium (eMC) or the British National Formulary (BNF).

Orlistat
Tirzepatide


### Orlistat

NICE recommends orlistat as an option for weight management and it can be prescribed in all settings, including primary care, if people meet the criteria in table 1.

Orlistat is taken orally and may be preferable to some people who prefer not to self-inject and are willing to accept the potential adverse effects associated with this medicine.

https://cks.nice.org.uk/topics/obesity/prescribing-information/orlistat/ 

Prescribe 120 mg to be taken with each of the three main meals per day. 
It can be taken immediately before, during, or up to 1 hour after a meal.

```{r}
#| label: create-orlistat_strength
#| include: false


df_orlistat_practice_strength <- df_orlistat_practice %>%
  mutate(strength =  gsub("\\D", "", bnf_name))

```

```{r}
#| label: create-regional-orlistat
#| include: false


df_orlistat_practice_month <- df_orlistat_practice_strength %>%
  group_by(month,strength,regional_team) %>%
  summarise(
            items=sum(items),
            regional_team = last(regional_team ))  %>%
  ungroup() %>%
  inner_join(df_region_stats,by=join_by(regional_team ==regional_team_id,month)) %>%
  mutate(rateper1000= items/total_list_size*1000)

```

Y55 (Midlands and East of England) and Y57 (South of ENgland) are now defunct. 

```{r}
#| label: identify-max-NA-region-date 
#| include: false


na_date_max <- df_orlistat_practice_month %>%
  filter(is.na(region)) %>%
  slice_max(month) %>%
  select(month) %>%
  pull()
# 2017-08-01
```


```{r}
#| label: remove-dates-before-cutoff
#| include: false

df_orlistat_practice_month <- df_orlistat_practice_month %>%
  filter(month>na_date_max)

```

```{r}
#| label: plot-orlistat
#| include: false
plot_orlistat_region <- df_orlistat_practice_month %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
      facet_wrap(vars(region)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    "orlistat",
    "orlistat_region.png"),
  plot_orlistat_region,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

##### low strength only

plot_orlistat_region_low <- df_orlistat_practice_month %>%
  filter(strength==60) %>%
      ggplot(aes(x = month, y = rateper1000)) +
      facet_wrap(vars(region)) +
        geom_line(color="blue") +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    "orlistat",
    "orlistat_region_low_strength.png"),
  plot_orlistat_region_low,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)


