---
title: "Obesity and GLP-1s"
validate-yaml: false
format: 
  html:
    fontsize: 11px
    mainfont: "Arial"
comments:
  enabled: true  
---

```{r}
#| label: load-packages
#| include: false
library(dplyr)
library(readr)
library(here)
library(glue)
library(tidyr)
library(stringr)
library(scales) ## format label_number
library(gt) ## gt table
library(ggplot2)
library(fpp2) # Forecasting: Principles and Practice" (2nd Edition)
library(lubridate) # interval
library(patchwork)
library(tibble)
```

```{r}
#| label: load-raw-data-minor-cleaning
#| include: false
date_tirzepatide_ng <- as.Date("2024-12-23")
date_tirzepatide_diab <- as.Date("2023-10-25")

df_normalised_prescribing <- read_csv(here::here(
  "data",
  "normalised_prescribing.csv.gz"
))
df_tirzepatide_practice <- read_csv(here::here(
  "data",
  "tirzepatide_practice.csv.gz"
))


### practice statistics data
df_practice_stats <- read_csv(here::here(
  "data",
  "practice_info_full.csv.gz"
)) ### as far back as 2015

### ccgs info
df_hscic_ccgs <- read_csv(here::here(
  "data",
  "practice_ccgs.csv.gz"
)) %>%
  select("code", "name", "stp_id", "regional_team_id", "org_type")

### region info
df_regions <- read_csv(here::here(
  "data",
  "NHS_England_Names_and_Codes_in_England.csv"
)) %>%
  rename(regional_team = NHSER24CDH, region = NHSER24NM) %>%
  dplyr::select(regional_team, region) %>%
  mutate(
    col_fill = c(
      "#8dabd371",
      "#e7b6e1",
      "#ffffb3",
      "#eeb35a38",
      "#8aebe693",
      "#b6e59b8c",
      "#f344444d"
    )
  )

regions <- df_regions %>%
  pull(region)

### QOF Obesity prevalence
df_qof_ob <- read_csv(here::here("data", "qof", "prevalence.csv"))

### QOF regions
df_qof_region <- read_csv(here::here("data", "qof", "geography.csv"))

df_qof_icbs <- df_qof_region %>%
  filter(year == "2024-25") %>%
  group_by(icb_ods_code) %>%
  summarise(icb_ods_code = last(icb_ods_code), icb_name = last(icb_name)) %>%
  mutate(
    icb_name = gsub("Integrated Care Board", "ICB", icb_name),
    # icb_name = gsub("ICB","",icb_name),
    #   icb_name = gsub("NHS ","",icb_name),
    icb_name = str_wrap(icb_name, width = 33)
  )

df_icb_stats_sicbl <- df_practice_stats %>%
  left_join(df_hscic_ccgs, by = join_by(pct_id == code)) %>%
  group_by(stp_id, month) %>%
  summarise(total_list_size = sum(total_list_size, na.rm = TRUE)) %>%
  drop_na(stp_id)
```

```{r}
#| label: tirzepitide-cleaning
#| include: false
df_tirzepatide_practice_strength <- df_tirzepatide_practice %>%
  mutate(
    strength = gsub("[^0-9/.]", "", bnf_name),
    strength = gsub("2.4", "", strength),
    strength = gsub("/", "mg / ", strength),
    strength = glue("{strength}ml")
  )

df_tirzepatide_practice_strength_month <- df_tirzepatide_practice_strength %>%
  left_join(
    df_normalised_prescribing %>% select(practice, stp, month),
    by = join_by(practice, month)
  ) %>%
  left_join(df_regions) %>%
  group_by(month, strength, region, stp) %>%
  summarise(
    items = sum(items),
    stp = last(stp),
    region = last(region)
  ) %>%
  ungroup() %>% ##5634
  inner_join(df_icb_stats_sicbl, by = join_by(stp == stp_id, month)) %>%
  inner_join(df_qof_icbs, by = join_by(stp == icb_ods_code)) %>%
  mutate(rateper1000 = items / total_list_size * 1000) ##5634


df_tirzepatide_practice_month <- df_tirzepatide_practice %>%
  left_join(
    df_normalised_prescribing %>% select(practice, stp, month),
    by = join_by(practice, month)
  ) %>%
  left_join(df_regions) %>%
  group_by(month, region, stp) %>%
  summarise(
    items = sum(items),
    stp = last(stp),
    region = last(region)
  ) %>%
  ungroup() %>% ##963
  inner_join(df_icb_stats_sicbl, by = join_by(stp == stp_id, month)) %>%
  inner_join(df_qof_icbs, by = join_by(stp == icb_ods_code)) %>%
  mutate(rateper1000 = items / total_list_size * 1000) ##963

df_tirzepatide_practice_strength_month_plot <- tibble(
  df_tirzepatide_practice_strength_month %>% select(region)
) %>%
  mutate(
    date_dm = as.POSIXct(date_tirzepatide_diab),
    date_ng = as.POSIXct(date_tirzepatide_ng)
  )
```


# OpenPrescribing Tirzepatide and Obesity Protocol
	

GitHub repository: https://github.com/andrewscolm/obesity_glp1 

### Project team / authors

Colm Andrews
Amy Gimma
Will Hulme
Elizabeth Morris 
Nerys Astbury
Rich Croker
Andrew Brown
Andrea Schaffer



## Background

### What is the research question?

How has prescribing of obesity medicines in primary care in England changed over time? And how does prescribing vary by ICB? Do ICBs with the highest obesity rates also have
the highest rates of GLP-1 prescribing?

### What is already known about the problem?

As of the most recent Health Survey for England in 2022, 29% of adults in England were living with obesity and 64% of adults were overweight or living with obesity.1 
The National Institute for Health and Care Excellence (NICE) recommends the use of pharmaceutical interventions for diabetes and weight management in some cases. In England, tirzepatide and orlistat are available for weight management through the NHS in primary, specialist, and secondary care settings, while liraglutide and semaglutide are available through specialist or secondary care settings for weight management. Orlistat is also available in pharmacies at low doses.4 

### What are the gaps in knowledge?

Tirzepatide use continues to increase in primary care settings in England and orlistat continues to be prescribed for some patients. Despite this, to date little has been published about the use of tirzepatide in primary care. 

### How will this work address these gaps?

We aim to use dispensing data from the English Prescribing Dataset (EPD) to describe the patterns of use of the weight medications tirzepatide and orlistat. Understanding variation in uptake of weight medications may help identify inequities in access, and differences in implementation of national guidance, during the rollout of weight management pathways in England.

### Objectives 

#### Primary Objectives

Describe tirzepatide prescribing by GPs in England, how it has changed over time, and how it varies across Integrated Care Boards.
Secondary Objectives

i) Describe how tirzepatide prescribing varies by obesity rate at the level of Integrated Care Boards. 
ii) Describe the impact of tirzepatide prescribing on the prescribing of orlistat.


## Methods 

### Study Design

Study type: A descriptive study giving monthly rates of i) tirzepatide and ii) orlistat prescribing over time and across ICBs.

Index date: i) Time trends will be monthly, from January 2023 to the most recent available full month. ii) Analysis of prescribing rates per obesity prevalence will be from January 2024 to December 2025 with the 2024/25 obesity prevalence as the denominator. 

### Data sources

Data source
OpenPrescribing – monthly prescribing (dispensing) of all medicines in England
 QOF obesity register – yearly practice-level data on people with obesity

### Study Population 

#### Inclusion / Exclusion Criteria

We will extract all available prescribing data, limited to institutions with setting code 4 - general practices, according to the NHS Digital dataset of practice characteristics(9).This excludes all other organisations such as prisons and out-of-hours services as they are not represented fully or consistently in our dataset since many of these prescriptions would not be dispensed in community pharmacies.

### Drug Definition

Tirzepatide will be defined by BNF codes starting 0601023AZ. All strengths will be included in the initial analysis, but the final analysis will be restricted to strengths included in the BNF guidance (namely 2.5mg/0.6ml, 5mg/0.6ml, 7.5mg/0.6ml, 10mg/0.6ml, 12.5mg/0.6ml and 15mg/0.6ml). 

Orlistat will be defined by BNF codes starting 0405010P0. All strengths will be included in the initial analysis, but the final analysis will be restricted to 120mg strength as indicated in the BNF guidance.

For each month tirzepatide and orlistat dispensing will be extracted at the practice level and aggregated up to ICB and regional levels.

### Study Measures

We will use GP data from OpenPrescribing to extract monthly data for the following measures:
i) Rate of tirzepatide prescribing per 1000 registered patients
ii) Rate of tirzepatide prescribing per 1000 obesity register size
iii) Rate of orlistat prescribing per 1000 registered patients
iv) Rate of orlistat prescribing per 1000 obesity register size

### Covariates 

The above described measures will be stratified by the following:
Geographic:
Region
Integrated Care Board

### Statistical Analysis 

We will use descriptive plots to show i) prescribing rates over time ii) the variation of prescribing rates within ICBs.

### Limitations 
This study only captures medications prescribed in a primary care setting. It does not capture prescribing via tier 3 weight management services or via private prescribing. OpenPrescribing data consists of the openly available English Prescribing dataset (EPD) which is aggregated at practice level and does not include any patient information. We are unable to link this with person-level data. As such we are unable to investigate the impact of inequalities on prescribing rates.  

The eligibility criteria for the QOF obesity register is not consistent year to year. Most QOF indicators were suspended between 2021 and April 2022(11). The QOF obesity is released yearly whereas our dispensing data was monthly. The QOF obesity register is not directly comparable longitudinally. We are, therefore, unable to look at QOF obesity register dates over multiple years. The  QOF obesity register likely underestimate true obesity prevalence and 


Tirzepatide may be prescribed for type 2 diabetes, obesity/weight management, possibly both. The English Prescribing Dataset does not include indication-level prescribing data. We are, therefore, unable to tell the indication for treatment. 

## Results

Table Shells / Mockup Figures
Example plots:
 i) prescribing rates over time

 ii) the variation of prescribing rates within ICBs. This example would be amended to show prescribing rate (x-axis) per practice (blue dot), overall density of prescribing (blue-scale background) for each ICB (y-axis) 

We are aiming for a total of 6 figures, tables or boxes (with additionals included in the supplementary materials). 

Box 1: changes in NICE recommendations

Figure 1A: Tirzepatide dispensing per 1000 registered patients - England
```{r}
#| echo: false
#| label: fig-1-a-dispensing-per-1000-registered-patients
#| fig-cap: "Tirzepatide dispensing per 1000 registered patients - England"
#| warning: false
```



Figure 1B: Tirzepatide dispensing per 1000 Obesity register - England
```{r}
#| echo: false
#| label: fig-1-b-dispensing-per-1000-obesity-register
#| fig-cap: Tirzepatide dispensing per 1000 Obesity register - England
#| warning: false
```

Figure 2: Tirzepatide dispensing per 1000 list size ICB
```{r}
#| echo: false
#| label: fig-2-dispensing-per-1000-list-size
#| fig-cap: "Tirzepatide dispensing per 1000 list size ICB"
#| warning: false
```

Figure 3. Tirzepatide dispensing per 1000 registered patients - England by aggregated strength

```{r}
#| echo: false
#| label: fig-3-dispensing-per-1000-reg-patients-by-strength
#| fig-cap: "Tirzepatide dispensing per 1000 registered patients - England by aggregated strength"
#| warning: false
# Figure 4
plot_tirzepatide_region_strengths <- df_tirzepatide_practice_strength_month %>%
  ggplot(aes(x = month, y = rateper1000, color = strength)) +
  geom_vline(
    xintercept = as.POSIXct(date_tirzepatide_diab),
    linetype = "dashed"
  ) +
  geom_vline(
    xintercept = as.POSIXct(date_tirzepatide_ng),
    linetype = "dotted"
  ) +
  facet_wrap(vars(icb_name)) +
  geom_line() +
  scale_y_continuous(labels = label_comma()) +
  theme(axis.text.x = element_text(angle = 90)) +
  ggtitle(glue("Tirzepatide items per 1000 list size")) +
  xlab("") +
  ylab("Rate per 1000 list size")

plot_tirzepatide_region_strengths
```


Figure 4. Orlistat 60mg dispensing per 1000 list size England (with tirzepatide guidance change dates)

```{r}
#| echo: false
#| label: fig-4-orlistat-per-1000-list-size
#| fig-cap: "Orlistat 60mg dispensing per 1000 list size England (with tirzepatide guidance change dates)"
#| warning: false
#| 
#plot_orlistat_icb
```

Figure 5. Variation of tirzepatide prescribing rates within ICBs
```{r}
#| echo: false
#| label: fig-4-tirzepatide-ICB-prescribing-variation
#| fig-cap: "Variation of tirzepatide prescribing rates within ICBs"
#| warning: false
```

Supplementary 
Tirzepatide dispensing per 1000 registered patients - ICB by aggregated strength
Tirzepatide dispensing per 1000 Obesity register - ICB
Maybe Correlation of registered patients and QOF obesity register A) at ICB level, B) (optionally) at practice level.       

Orlistat 60mg dispensing per 1000 list size ICB (with tirzepatide guidance change dates)     



References 


1.	England, N. H. S. NHS England » Obesity. https://www.england.nhs.uk/ourwork/prevention/obesity/.
2.	Health Survey for England, 2022 Part 2. NHS England Digital https://digital.nhs.uk/data-and-information/publications/statistical/health-survey-for-england/2022-part-2.
3.	Moiz, A. et al. Mechanisms of GLP-1 receptor agonist-induced weight loss: A review of central and peripheral pathways in appetite and energy regulation. Am. J. Med. 138, 934–940 (2025).
4.	NICE Guideline 246: Overweight and Obesity Management. https://www.nice.org.uk/guidance/ng246/resources/overweight-and-obesity-management-pdf-66143959958725 (2025).

