---
title: "Obesity and GLP-1s"
format: 
  html:
    fontsize: 11px
    mainfont: "Arial"
---

```{r}
#| label: load-packages
#| include: false

library(dplyr)
library(readr)
library(here)
library(glue)
library(tidyr)
library(stringr)
library(scales) ## format label_number
library(gt) ## gt table
library(ggplot2)
library(fpp2) # Forecasting: Principles and Practice" (2nd Edition)
library(lubridate) # interval
library(patchwork)
library(tibble)
```

```{r}
#| label: import-data
#| include: false

directory_name <- "data"
date_tirzepatide_ng <-as.Date("2024-12-23")
date_tirzepatide_diab <-as.Date("2023-10-25")

label_number_n <- label_number(1, 1, big.mark=",")
label_perc_n <- label_percent(accuracy =.0001)

#### practice level orlistat data
df_orlistat_practice <- read_csv(here::here(directory_name,"orlistat_practice.csv.gz")) 

#### practice level tirzepatide data
df_tirzepatide_practice <- read_csv(here::here(directory_name,"tirzepatide_practice.csv.gz")) 

### practice statistics data
df_practice_stats <- read_csv(here::here(directory_name,"practice_info_full.csv.gz")) ### as far back as 2015

df_normalised_prescribing <- read_csv(here::here(directory_name,"normalised_prescribing.csv.gz"))

### ccgs info
df_hscic_ccgs <- read_csv(here::here(directory_name,"practice_ccgs.csv.gz")) %>%
  select("code","name","stp_id", "regional_team_id","org_type") 

### region info
df_regions <- read_csv(here::here("data","NHS_England_Names_and_Codes_in_England.csv")) %>%
  rename(regional_team = NHSER24CDH ,region = NHSER24NM) %>%
  dplyr::select(regional_team,region) %>%
        mutate(col_fill=c(
    "#8dabd371",
   "#e7b6e1",
    "#ffffb3",
    "#eeb35a38",
   "#8aebe693",
    "#b6e59b8c",
    "#f344444d"
  )) 

regions <- df_regions %>%
  pull(region)

### QOF Obesity prevalence
df_qof_ob <-  read_csv(here::here("data", "qof", "prevalence.csv"))

### QOF regions
df_qof_region <-  read_csv(here::here("data", "qof", "geography.csv"))

df_qof_icbs <- df_qof_region %>% 
  filter(year=="2024-25") %>%
  group_by(icb_ods_code) %>%
  summarise(icb_ods_code = last(icb_ods_code),
  icb_name= last(icb_name)) %>%
    mutate(icb_name = gsub("Integrated Care Board","ICB",icb_name),
    # icb_name = gsub("ICB","",icb_name),
#   icb_name = gsub("NHS ","",icb_name),
    icb_name = str_wrap(icb_name, width = 33))
```

```{r}
#| label: create-regional-stats
#| include: false

### join region information to the practice stats
df_region_stats <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  left_join(df_regions,by=join_by(regional_team_id ==regional_team )) %>%
  group_by(regional_team_id,month) %>%
  summarise(total_list_size=sum(total_list_size, na.rm = TRUE),
            regional_team_id = last(regional_team_id ),
              region = last(region ))

```

For historic reasons Integrated Care Boards (ICBs) are labelled as stp_id [Sustainability and Transformation Partnerships (STPs)]. There are multiple ways of identifying ICBs (see https://docs.google.com/document/d/1ZpfwiU_UnNX4T7y-lGPD-8i6rof69O8i-aX6xNy4li8/edit?tab=t.0)

```{r}
#| label: create-icb-stats
#| include: false

### join icb information to the practice stats
df_icb_stats <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  group_by(stp_id,month) %>%
  summarise(total_list_size=sum(total_list_size, na.rm = TRUE))

```

Quite a few practices in practice stats are missing STP info. How many are after the change in regions? (Y55 (Midlands and East of England) and Y57 (South of England) are now defunct)

```{r}
#| label: identify-max-NA-region-date 
#| include: false


na_date_max <- df_orlistat_practice %>%
  group_by(month,regional_team) %>%
  summarise(
            items=sum(items),
            regional_team = last(regional_team ))  %>%
  ungroup() %>%
  inner_join(df_region_stats,by=join_by(regional_team ==regional_team_id,month)) %>%
  mutate(rateper1000= items/total_list_size*1000) %>%
  filter(is.na(region)) %>%
  slice_max(month) %>%
  select(month) %>%
  pull()
# 2017-08-01
```


```{r}
#| label: identify-practice-stats-missing-stp
#| include: false

df_icb_stats_missing_stp <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  filter(month>na_date_max)  %>%
  filter(is.na(stp_id))

nrow(df_icb_stats_missing_stp)
# 134396

## joining on sicbl instead of pct_id
df_icb_stats_missing_stp_sicbl <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(sicbl ==code)) %>%
  filter(month>na_date_max)  %>%
  filter(is.na(stp_id))

nrow(df_icb_stats_missing_stp_sicbl)
# 2855
```

```{r}
#| label: create-icb-stats-from-sicbl
#| include: false

## remove NAs
df_icb_stats_sicbl <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  group_by(stp_id,month) %>%
  summarise(total_list_size=sum(total_list_size, na.rm = TRUE)) %>%
  drop_na(stp_id)

```


https://cks.nice.org.uk/topics/obesity/prescribing-information/

Important aspects of prescribing information relevant to primary healthcare are covered in this section specifically for the drugs recommended in this CKS topic. For further information on contraindications, cautions, drug interactions, and adverse effects, see the electronic Medicines Compendium (eMC) or the British National Formulary (BNF).

Orlistat
Tirzepatide


### Orlistat

NICE recommends orlistat as an option for weight management and it can be prescribed in all settings, including primary care, if people meet the criteria in table 1.

Orlistat is taken orally and may be preferable to some people who prefer not to self-inject and are willing to accept the potential adverse effects associated with this medicine.

https://cks.nice.org.uk/topics/obesity/prescribing-information/orlistat/ 

Prescribe 120 mg to be taken with each of the three main meals per day. 
It can be taken immediately before, during, or up to 1 hour after a meal.



Some orlistat prescribing practices are missing STP info. Are they before the change in region?


What geography info is available?

`normalised_prescribing` has stp (ICB), pct (sicbl), regional_team and practice; 

`ccgs` has stp_id (ICB), regional_team_id, code (CCG (sicbl) / PCT (sicbl) / Unknown (mainly commisioning hubs))

`practice_stats` has practice, pct_id (sicbl)

`practices` has code (practice), ccg_id (sicbl), pcn_id (PCN)

`stp` has code (ICB) and name (name of ICB)

`prescribing_setting` has no geography info  

`df_tirzepatide` has practice and regional_team 


```{r}
#| label: missing-orlistat_stp
#| include: false


 missing_stp <- df_orlistat_practice %>%
  filter(is.na(stp))

nrow(missing_stp)
# 28775
 
 missing_stp_after_region_change <- df_orlistat_practice %>%
  filter(month>na_date_max) %>%
  filter(is.na(stp))

nrow(missing_stp_after_region_change)
# 1424

#percentage missing
nrow(missing_stp_after_region_change)  / nrow(df_orlistat_practice %>% filter(month>na_date_max)) * 100
# 0.24%


#  View(missing_stp_after_region_change)
# practices from different regions up to Feb 2020

 missing_stp_after_2023 <- df_orlistat_practice %>%
  filter(month>=as.Date("2023-01-01")) %>%
  filter(is.na(stp))

nrow(missing_stp_after_2023)

```

Are they the same practices as practice stats?

```{r}
#| label: missing-orlistat_and_practice
#| include: false

df_orlistat_practice_with_stp <- df_orlistat_practice %>%
  filter(month>na_date_max) %>%
  drop_na(stp)
 
nrow(df_orlistat_practice_with_stp)
# 583290

df_orlistat_practice_with_stp_and_stats <- df_orlistat_practice_with_stp %>%
  inner_join(df_icb_stats_sicbl,by = join_by(stp ==stp_id,month))

nrow(df_orlistat_practice_with_stp_and_stats)
# 497925

nrow(df_orlistat_practice_with_stp) - nrow(df_orlistat_practice_with_stp_and_stats)
# 85365


### which practices have orlistat stp but no practice stats stp?
df_orlistat_practice_with_stp_no_stats <- df_orlistat_practice_with_stp %>%
  anti_join(df_orlistat_practice_with_stp_and_stats, by=join_by(stp,month))

# View(df_orlistat_practice_with_stp_no_stats)

```



```{r}
#| label: create-orlistat_strength
#| include: false


df_orlistat_practice_strength <- df_orlistat_practice%>%
  mutate(strength =  gsub("\\D", "", bnf_name),
  strength = glue("{strength}mg"))

```


```{r}
#| label: create-icb-orlistat
#| include: false

#### pct_id
df_orlistat_icb_month_pct_id <- df_orlistat_practice_strength %>%
  group_by(month,strength,stp) %>%
  summarise(
            items=sum(items),
            stp = last(stp ),
            regional_team = last(regional_team))  %>%
  ungroup()  %>%
  filter(month>=as.Date("2023-01-01"))
  
  orlistat_rows<-nrow(df_orlistat_icb_month_pct_id)
  
  df_orlistat_icb_month_pct_id <- df_orlistat_icb_month_pct_id %>%
  inner_join(df_icb_stats,by=join_by(stp ==stp_id,month)) %>%
  inner_join(df_regions) %>%
  mutate(rateper1000= items/total_list_size*1000)

  orlistat_icb_rows<-nrow(df_orlistat_icb_month_pct_id)

  dropped_icb_months <- orlistat_rows - orlistat_icb_rows
 #0


### sicbl
df_orlistat_icb_month_orig <- df_orlistat_practice_strength %>%
  group_by(month,strength,stp) %>%
  summarise(
            items=sum(items),
            stp = last(stp ),
            regional_team=last(regional_team))  %>%
  ungroup()  %>%
  filter(month>=as.Date("2023-01-01"))
  
  orlistat_rows<-nrow(df_orlistat_icb_month_orig)
  
  df_orlistat_icb_month <- df_orlistat_icb_month_orig %>%
  inner_join(df_icb_stats_sicbl,by=join_by(stp ==stp_id,month)) %>%
  inner_join(df_regions) %>%
  inner_join(df_qof_icbs,by =join_by(stp==icb_ods_code)) %>%
  mutate(rateper1000= items/total_list_size*1000) %>%
  drop_na(stp)

  orlistat_icb_rows<-nrow(df_orlistat_icb_month)

  dropped_icb_months <- orlistat_rows - orlistat_icb_rows
 #0

```

```{r}
#| label: orlistat-rate-range
#| include: false

max_orlistat_120<- df_orlistat_icb_month %>%
  filter(month == as.Date("2025-12-01"),
  strength == "120mg") %>%
  slice_max(rateper1000,n=1)

min_orlistat_120 <- df_orlistat_icb_month %>%
  filter(month == as.Date("2025-12-01"),
  strength == "120mg") %>%
  slice_min(rateper1000,n=1)


max_orlistat_60<- df_orlistat_icb_month %>%
  filter(month == as.Date("2025-12-01"),
  strength == "60mg") %>%
  slice_max(rateper1000,n=1)

min_orlistat_60 <- df_orlistat_icb_month %>%
  filter(month == as.Date("2025-12-01"),
  strength == "60mg") %>%
  slice_min(rateper1000,n=1)


max_y_orlistat_120 <- df_orlistat_icb_month %>%
  filter(strength == "120mg") %>%
  slice_max(rateper1000,n=1) %>%
  select(rateper1000) %>%
  pull()

max_y_orlistat_60 <- df_orlistat_icb_month %>%
  filter(strength == "60mg") %>%
  slice_max(rateper1000,n=1) %>%
  select(rateper1000) %>%
  pull()

```

```{r}
#| label: plot-orlistat
#| include: false

plot_orlistat_icb <- df_orlistat_icb_month %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat items per 1000 list size")) +
            xlab("") +
            ylab("Rate per 1000 list size")
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "orlistat",
    "orlistat_icb.png"),
  plot_orlistat_icb,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

##### low strength only

plot_orlistat_icb_low <- df_orlistat_icb_month %>%
  filter(strength=="60mg") %>%
      ggplot(aes(x = month, y = rateper1000)) +
      facet_wrap(vars(icb_name)) +
        geom_line(color="blue") +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat items per 1000 list size")) +
            xlab("") +
            ylab("Rate per 1000 list size")
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "orlistat",
    "orlistat_icb_low_strength.png"),
  plot_orlistat_icb_low,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

### by region
for (region_name in regions){

plot_orlistat_icb_region <- df_orlistat_icb_month %>%
  filter(region == region_name) %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat items per 1000 list size: {region_name}")) +
            xlab("") +
            ylab("Rate per 1000 list size")
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "orlistat",
    glue("orlistat_icb_{region_name}.png")),
  plot_orlistat_icb_region,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

}


###  region patchwork
for (region_name in regions){

assign(glue("plot_orlistat_icb_region_{region_name}"), df_orlistat_icb_month %>%
  filter(region == region_name) %>%
   mutate(icb_name = factor(icb_name, levels = c(levels(as.factor(icb_name)),""," ","  ","    ","     ")[1:(ceiling(length(c(levels(as.factor(icb_name))))/6)*6)])) %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
      facet_wrap(vars(icb_name),ncol=6,nrow=2, drop = FALSE) +
        geom_line() +
          scale_y_continuous(labels = label_comma(),limits =c(0,max_y_orlistat_120)) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat items per 1000 list size: {region_name}")) +
            xlab("") +
            ylab("Rate per 1000 list size")  +
  theme_minimal())
          
}

 plot_orlistat_icb_region_patchwork <- wrap_plots(
  `plot_orlistat_icb_region_East of England`,
  plot_orlistat_icb_region_London,
  plot_orlistat_icb_region_Midlands,
  `plot_orlistat_icb_region_North East and Yorkshire`,
  `plot_orlistat_icb_region_North West`,
  `plot_orlistat_icb_region_South East`,
  `plot_orlistat_icb_region_South West`,
  ncol=1, heights = c(1,1,2,1,1,1,2))

  
ggsave(
  filename = here::here(
    "output",
    "icb",
    "orlistat",
    glue("plot_orlistat_icb_region_patchwork.png")),
  plot_orlistat_icb_region_patchwork,
  dpi = 800,
  width = 60,
  height = 60,
  units = "cm"
)




### low strength only

###  region patchwork
for (region_name in regions){

assign(glue("plot_orlistat_low_icb_region_{region_name}"), df_orlistat_icb_month %>%
  filter(region == region_name,
         strength == "60 mg") %>%
   mutate(icb_name = factor(icb_name, levels = c(levels(as.factor(icb_name)),""," ","  ","    ","     ")[1:(ceiling(length(c(levels(as.factor(icb_name))))/6)*6)])) %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
      facet_wrap(vars(icb_name),ncol=6,nrow=2, drop = FALSE) +
        geom_line() +
          scale_y_continuous(labels = label_comma(),limits =c(0,max_y_orlistat_120)) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat items per 1000 list size: {region_name}")) +
            xlab("") +
            ylab("Rate per 1000 list size")  +
  theme_minimal())
          
}

 plot_orlistat_icb_region_patchwork <- wrap_plots(
  `plot_orlistat_low_icb_region_East of England`,
  plot_orlistat_low_icb_region_London,
  plot_orlistat_low_icb_region_Midlands,
  `plot_orlistat_low_icb_region_North East and Yorkshire`,
  `plot_orlistat_low_icb_region_North West`,
  `plot_orlistat_low_icb_region_South East`,
  `plot_orlistat_low_icb_region_South West`,
  ncol=1, heights = c(1,1,2,1,1,1,2))

  
ggsave(
  filename = here::here(
    "output",
    "icb",
    "orlistat",
    glue("plot_orlistat_low_icb_region_patchwork.png")),
  plot_orlistat_icb_region_patchwork,
  dpi = 800,
  width = 60,
  height = 60,
  units = "cm"
)




```

### Tirzepatide

```{r}
#| label: tirzepatide-strength
#| include: false

df_tirzepatide_practice_strength <- df_tirzepatide_practice %>%
  mutate(strength = gsub("[^0-9/.]", "", bnf_name),
  strength = gsub("2.4", "", strength),
  strength = gsub("/", "mg / ", strength),
  strength = glue("{strength}ml"))






```


How many practices are missing stp info using `normalised_prescribing.stp`

```{r}
#| label: tirzepatide-missing-stps
#| include: false

nrow(df_tirzepatide_practice_strength)
# 557408
nrow(df_tirzepatide_practice_strength %>% 
  left_join(df_normalised_prescribing %>% select(practice,stp,month), by =join_by(practice,month)))
# 557408
 
df_tirzepatide_practice_strength %>% 
  left_join(df_normalised_prescribing %>% select(practice,stp,month), by =join_by(practice,month))  %>%
  filter(is.na(stp))
### No practices missing stp!
```



```{r}
#| label: create-regional-tirzepatide
#| include: false


df_tirzepatide_practice_strength_month <- df_tirzepatide_practice_strength %>% 
  left_join(df_normalised_prescribing %>% select(practice,stp,month), by =join_by(practice, month))  %>% 
  left_join(df_regions) %>%
  group_by(month,strength,region,stp) %>%
  summarise(
            items=sum(items),
            stp = last(stp),
            region = last(region ))  %>%
  ungroup() %>% ##5634
  inner_join(df_icb_stats_sicbl,by=join_by(stp ==stp_id,month)) %>%
  inner_join(df_qof_icbs,by =join_by(stp==icb_ods_code)) %>%
  mutate(rateper1000= items/total_list_size*1000) ##5634



df_tirzepatide_practice_month <- df_tirzepatide_practice %>%
    left_join(df_normalised_prescribing %>% select(practice,stp,month), by =join_by(practice, month))  %>%
  left_join(df_regions) %>%
  group_by(month,region,stp) %>%
  summarise(
            items=sum(items),
            stp = last(stp),
            region = last(region ))  %>%
  ungroup() %>% ##963
  inner_join(df_icb_stats_sicbl,by=join_by(stp ==stp_id,month)) %>%
  inner_join(df_qof_icbs,by =join_by(stp==icb_ods_code)) %>%
  mutate(rateper1000= items/total_list_size*1000) ##963

```


```{r}
#| label: rate-range-tirzepatide
#| include: false

max_tirzepatide<- df_tirzepatide_practice_month %>%
  filter(month == as.Date("2025-12-01")) %>%
  slice_max(rateper1000,n=1)

min_tirzepatide<- df_tirzepatide_practice_month %>%
  filter(month == as.Date("2025-12-01")) %>%
  slice_min(rateper1000,n=1)

max_y_tirzepatide <- df_tirzepatide_practice_month %>%
  slice_max(rateper1000,n=1) %>%
  select(rateper1000) %>%
  pull()

max_y_tirzepatide_strength <- df_tirzepatide_practice_strength_month %>%
  slice_max(rateper1000,n=1) %>%
  select(rateper1000) %>%
  pull()


```

```{r}
#| label: plot-tirzepatide
#| include: false

df<-tibble(df_tirzepatide_practice_strength_month %>% select(region)) %>%
  mutate(date_dm = as.POSIXct(date_tirzepatide_diab),  date_ng = as.POSIXct(date_tirzepatide_ng ))


plot_tirzepatide_region_strengths <- df_tirzepatide_practice_strength_month %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
    geom_vline(xintercept=as.POSIXct(date_tirzepatide_diab), linetype="dashed") +
    geom_vline( xintercept=as.POSIXct(date_tirzepatide_ng ), linetype="dotted") +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))  +
            ggtitle(glue("Tirzepatide items per 1000 list size")) +
            xlab("") +
            ylab("Rate per 1000 list size")

          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "tirzepatide_by_strength",
    "tirzepatide_icb_strengths.png"),
  plot_tirzepatide_region_strengths,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

###  region patchwork
for (region_name in regions){

assign(glue("plot_tirzepatide_region_strengths_{region_name}"), df_tirzepatide_practice_strength_month %>%
  filter(region == region_name) %>%
   mutate(icb_name = factor(icb_name, levels = c(levels(as.factor(icb_name)),""," ","  ","    ","     ")[1:(ceiling(length(c(levels(as.factor(icb_name))))/6)*6)])) %>%
      ggplot(aes(x = month, y = rateper1000,colour=strength)) +
      facet_wrap(vars(icb_name),ncol=6,nrow=2, drop = FALSE) +
        geom_line() +
          scale_y_continuous(labels = label_comma(),limits =c(0,max_y_tirzepatide_strength)) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Tirzepatide items per 1000 list size: {region_name}")) +
            xlab("") +
            ylab("Rate per 1000 list size") +
  theme_minimal())
          
}

 plot_tirzepatide_region_strengths_patchwork <- wrap_plots(
  `plot_tirzepatide_region_strengths_East of England`,
  plot_tirzepatide_region_strengths_London,
  plot_tirzepatide_region_strengths_Midlands,
  `plot_tirzepatide_region_strengths_North East and Yorkshire`,
  `plot_tirzepatide_region_strengths_North West`,
  `plot_tirzepatide_region_strengths_South East`,
  `plot_tirzepatide_region_strengths_South West`,
  ncol=1, heights = c(1,1,2,1,1,1,2))

  
ggsave(
  filename = here::here(
    "output",
    "icb",
    "tirzepatide",
    glue("plot_tirzepatide_region_strengths_patchwork.png")),
  plot_tirzepatide_region_strengths_patchwork,
  dpi = 800,
  width = 60,
  height = 60,
  units = "cm"
)






##### all tirzepatide

plot_tirzepatide_region <- df_tirzepatide_practice_month %>%
      ggplot(aes(x = month, y = rateper1000)) +
    geom_vline(xintercept=as.POSIXct(date_tirzepatide_diab), linetype="dashed") +
    geom_vline( xintercept=as.POSIXct(date_tirzepatide_ng ), linetype="dotted") +
      facet_wrap(vars(icb_name)) +
        geom_line(color="blue") +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))  +
            ggtitle(glue("Tirzepatide items per 1000 list size")) +
            xlab("") +
            ylab("Rate per 1000 list size")

          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "tirzepatide_all",
    "tirzepatide_icb.png"),
  plot_tirzepatide_region,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

### by region

for (region_name in regions){

plot_tirzepatide_icb_region <- df_tirzepatide_practice_strength_month %>%
  filter(region == region_name) %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Tirzepatide items per 1000 list size: {region_name}")) +
            xlab("") +
            ylab("Rate per 1000 list size")
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "tirzepatide_by_strength",
    glue("tirzepatide_icb_{region_name}.png")),
  plot_tirzepatide_icb_region,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

plot_tirzepatide_icb_region <- df_tirzepatide_practice_month %>%
  filter(region == region_name) %>%
      ggplot(aes(x = month, y = rateper1000)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Tirzepatide items per 1000 list size: {region_name}")) +
            xlab("") +
            ylab("Rate per 1000 list size")
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "tirzepatide_all",
    glue("tirzepatide_all_icb_{region_name}.png")),
  plot_tirzepatide_icb_region,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)




}

###  region patchwork
for (region_name in regions){

assign(glue("plot_tirzepatide_icb_region_{region_name}"), df_tirzepatide_practice_month %>%
  filter(region == region_name) %>%
   mutate(icb_name = factor(icb_name, levels = c(levels(as.factor(icb_name)),""," ","  ","    ","     ")[1:(ceiling(length(c(levels(as.factor(icb_name))))/6)*6)])) %>%
      ggplot(aes(x = month, y = rateper1000)) +
      facet_wrap(vars(icb_name),ncol=6,nrow=2, drop = FALSE) +
        geom_line() +
          scale_y_continuous(labels = label_comma(),limits =c(0,max_y_tirzepatide)) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Tirzepatide items per 1000 list size: {region_name}")) +
            xlab("") +
            ylab("Rate per 1000 list size")  +
  theme_minimal())
          
}

 plot_tirzepatide_icb_region_patchwork <- wrap_plots(
  `plot_tirzepatide_icb_region_East of England`,
  plot_tirzepatide_icb_region_London,
  plot_tirzepatide_icb_region_Midlands,
  `plot_tirzepatide_icb_region_North East and Yorkshire`,
  `plot_tirzepatide_icb_region_North West`,
  `plot_tirzepatide_icb_region_South East`,
  `plot_tirzepatide_icb_region_South West`,
  ncol=1, heights = c(1,1,2,1,1,1,2))

  
ggsave(
  filename = here::here(
    "output",
    "icb",
    "tirzepatide",
    glue("plot_tirzepatide_icb_region_patchwork.png")),
  plot_tirzepatide_icb_region_patchwork,
  dpi = 800,
  width = 60,
  height = 60,
  units = "cm"
)





```


```{r}
#| label: combine-orlistat-tirzepatide
#| include: false

df_orlistat_icb_month_120 <- df_orlistat_icb_month %>%
  filter(strength == "120mg") %>%
  reframe(month,region,stp,rateper1000_orlistat=rateper1000)


df_orlistat_tirzepatide <- df_orlistat_icb_month_120 %>%
  left_join(df_tirzepatide_practice_month %>% 
      reframe(month,region,stp,rateper1000_tirzepatide=rateper1000), by = join_by(month,stp,region)) %>%
  pivot_longer(cols = starts_with("rateper1000_"),
    names_to = "drug",
    names_prefix = "rateper1000_",
    values_to = "rateper1000") %>%
      inner_join(df_qof_icbs,by=join_by(stp==icb_ods_code)) %>%
      inner_join(df_regions)

```



```{r}
#| label: plot-orlistat-tirzepatide
#| include: false

plot_orlistat_tirzepatide <- df_orlistat_tirzepatide %>%
      ggplot(aes(x = month, y = rateper1000,color=drug)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat and tirzepatide items per 1000 list size")) +
            xlab("") +
            ylab("Rate per 1000 list size")
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "combined",
    "combined_orlistat_tirzepatide_icb.png"),
  plot_orlistat_tirzepatide,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)



plots <- df_orlistat_tirzepatide %>%
  arrange(region) %>%
  mutate(stp = factor(stp,levels = unique(stp))) %>%
  split(.$stp) %>%
  purrr::map(function(data_seg) {
  ggplot(data_seg,aes(x = month, y = rateper1000,color=drug)) +
  geom_line() +
  scale_y_continuous(limits=c(0,max(df_orlistat_tirzepatide$rateper1000,na.rm = TRUE)+0.001)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle =90)) +
  xlab("") +
  ylab("Rate per 1000 list size") +
  theme(plot.background = element_rect(fill = data_seg$col_fill),
  plot.title = element_text(size =8)) +
    ggtitle(data_seg$icb_name) +
  geom_vline(xintercept=as.POSIXct(date_tirzepatide_diab), linetype="dashed") +
  geom_vline( xintercept=as.POSIXct(date_tirzepatide_ng ), linetype="dotted") 
  })


#### legends
legend <- cowplot::get_legend(
  plots[[1]] +  
    theme(
      legend.position = "bottom",
      legend.key.size = unit(0.4, "lines"), 
      legend.spacing.y = unit(0.2, "cm")    
    )
) 

legend_region <- cowplot::get_legend(
ggplot(
df_orlistat_tirzepatide %>% 
mutate(region = case_when(region =="North East and Yorkshire" ~ "North East and Yorkshire", .default = region)), 
aes(x = rateper1000, y = icb_name)) +
geom_tile(aes(fill = region)) +
scale_fill_manual(values = c(
"London"            =       "#8dabd371",
"South East"        =      "#e7b6e1",
"South West"        =      "#ffffb3",
"Midlands"          =      "#eeb35a38",
"North East and Yorkshire" = "#8aebe693",
"East of England"        =  "#b6e59b8c",  
"North West"             =  "#f344444d"
))+ 
theme(
legend.byrow=TRUE,
legend.position = "bottom",
legend.key.size = unit(0.4, "lines"), 
legend.spacing.y = unit(0.2, "cm")  
)
)




plot_orlistat_tirzepatide_region_split <- wrap_plots(c(plots,list(legend),list(plot_spacer()),list(plot_spacer()),list(legend_region)),ncol=6,axes="collect",guides ="collect", heights=c(1,1,1,1,1,1,1,0.5)) & 
theme(legend.position = "none")

ggsave(
  filename = here::here(
  "output",
  "icb",
  "combined",
  glue("combined_orlistat_tirzepatide_icb_split.png")),
  plot_orlistat_tirzepatide_region_split,
dpi = 800,
width = 30,
height = 30,
units = "cm"
)

# ### by region
# for (region_name in regions){

# plot_orlistat_tirzepatide_region <- df_orlistat_tirzepatide %>%
#   filter(region == region_name) %>%
#       ggplot(aes(x = month, y = rateper1000,color=drug)) +
#       facet_wrap(vars(icb_name)) +
#         geom_line() +
#           scale_y_continuous(labels = label_comma()) +
#             theme(axis.text.x = element_text(angle =90)) +
#             ggtitle(glue("Orlistat and tirzepatide items per 1000 list size")) +
#             xlab("") +
#             ylab("Rate per 1000 list size")
          
# ggsave(
#   filename = here::here(
#     "output",
#     "icb",
#     "combined",
#     glue("combined_orlistat_tirzepatide_icb_{region_name}.png")),
#   plot_orlistat_tirzepatide_region,
#   dpi = 800,
#   width = 60,
#   height = 30,
#   units = "cm"
# )

# }


# ###  region patchwork
# for (region_name in regions){

# assign(glue("plot_orlistat_tirzepatide_region_{region_name}"), df_orlistat_tirzepatide %>%
#   filter(region == region_name) %>%
#    mutate(icb_name = factor(icb_name, levels = c(levels(as.factor(icb_name)),""," ","  ","    ","     ")[1:(ceiling(length(c(levels(as.factor(icb_name))))/6)*6)])) %>%
#       ggplot(aes(x = month, y = rateper1000,colour=drug)) +
#       facet_wrap(vars(icb_name),ncol=6,nrow=2, drop = FALSE) +
#         geom_line() +
#           scale_y_continuous(labels = label_comma(),limits =c(0,max_y_tirzepatide)) +
#             theme(axis.text.x = element_text(angle =90)) +
#             ggtitle(glue("Tirzepatide items per 1000 list size: {region_name}")) +
#             xlab("") +
#             ylab("Rate per 1000 list size")  +
#   theme_minimal())
          
# }

#  plot_orlistat_tirzepatide_region_patchwork <- wrap_plots(
#   `plot_orlistat_tirzepatide_region_East of England`,
#   `plot_orlistat_tirzepatide_region_London`,
#   `plot_orlistat_tirzepatide_region_Midlands`,
#   `plot_orlistat_tirzepatide_region_North East and Yorkshire`,
#   `plot_orlistat_tirzepatide_region_North West`,
#   `plot_orlistat_tirzepatide_region_South East`,
#   `plot_orlistat_tirzepatide_region_South West`,
#   ncol=1, heights = c(1,1,2,1,1,1,2))

  
# ggsave(
#   filename = here::here(
#     "output",
#     "icb",
#     "combined",
#     glue("combined_orlistat_tirzepatide_icb_patchwork.png")),
#   plot_orlistat_tirzepatide_region_patchwork,
#   dpi = 800,
#   width = 60,
#   height = 60,
#   units = "cm"
# )
```

#### QOF obesity prevalence

```{r}
#| label: obesity-prevalence
#| include: false

#### clean region
df_qof_region_clean <- df_qof_region %>% 
  filter(year=="2024-25") %>%
  group_by(icb_name) %>%
  summarise(icb_name = last(icb_name),
    icb_ods_code = last(icb_ods_code))


df_qof_ob_icb  <- df_qof_ob %>%
   left_join(df_qof_region) %>%
   group_by(year,icb_ods_code  ) %>%
   summarise(register=sum(register,na.omit=T),
      icb_list_size = sum(practice_list_size,na.omit=T),
      region_name=last(region_name),
      icb_ods_code  = last(icb_ods_code ),
      icb_name = last(icb_name)) %>%
   inner_join(df_qof_region_clean, by=join_by(icb_ods_code)) %>%
   mutate(month =as.POSIXct(paste0(substr(year, 1,4),"-01-01") ),
   icb_name = icb_name.y)  %>%
      pivot_longer(cols = c("register","icb_list_size"),
    names_to = "measure")
   

```




```{r}
#| label: combine-orlistat-tirzepatide-england
#| include: false

 df_orlistat_england <- df_orlistat_practice_strength %>%
  filter(strength == "120mg") %>%
  group_by(month,chemical) %>%
  summarise(items=sum(items))

 df_tirzepatide_england <- df_tirzepatide_practice %>%
  filter(bnf_name=="Mounjaro 2.5mg/0.5ml solution for injection pre-filled pens") %>%
  group_by(month,chemical) %>%
  summarise(items=sum(items))

df_icb_stats_england <- df_icb_stats %>% 
  group_by(month) %>%
  summarise(total_list_size = sum(total_list_size))

df_orlistat_tirzepatide_england <- df_orlistat_england %>%
  rows_append(df_tirzepatide_england) %>%
  inner_join(df_icb_stats_england) %>%
  mutate(rateper1000 = items / total_list_size * 1000)



plot_orlistat_tirzepatide_england <- df_orlistat_tirzepatide_england %>%
      ggplot(aes(x = month, y = rateper1000,color=chemical )) +
        geom_line() +
            geom_vline(xintercept=as.POSIXct(date_tirzepatide_diab), linetype="dashed") +
            annotate("text", y = 3.5, x = as.POSIXct(date_tirzepatide_diab-35), label = "NICE Diabetes Guidance",angle = 90) +
    geom_vline( xintercept=as.POSIXct(date_tirzepatide_ng ), linetype="dotted") +
    annotate("text", y = 3.5, x = as.POSIXct(date_tirzepatide_ng -35), label = "NICE Obesity Guidance",angle = 90) +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat and tirzepatide items per 1000 list size")) +
            xlab("") +
            ylab("Rate per 1000 list size") + theme_classic()
          
ggsave(
  filename = here::here(
    "output",
    "England",
    "combined",
    "combined_orlistat_tirzepatide_icb.png"),
  plot_orlistat_tirzepatide_england,
  dpi = 800,
  width = 30,
  height = 15,
  units = "cm"
)





####### QOF
df_qof_ob_england <- df_qof_ob_icb %>%
  filter(measure =="register") %>%
  group_by(year)  %>%
  summarise(register=sum(value))

### tofix
# df_orlistat_tirzepatide_england_qof<- df_orlistat_tirzepatide_england %>%
#   inner_join(df_qof_ob_england, by ="month")


```




```{r}
#| label: plot-obesity-prevalence
#| include: false


plot_qof_ob_icb <- df_qof_ob_icb %>%
  filter(measure=="register") %>%
      ggplot(aes(x = month, y = value)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "qof_obesity_icb_measure.png"),
  plot_qof_ob_icb,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)


### plot with list size
plot_qof_ob_icb_measure <- df_qof_ob_icb %>%
      ggplot(aes(x = month, y = value,colour = measure)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "qof_obesity_icb_measure.png"),
  plot_qof_ob_icb,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)



```

Using as 2024/25 QOF obesity register as the denominator

```{r}
#| label: combine-QOF-and-OP-data 
#| include: false

df_qof_ob_icb_wide  <- df_qof_ob %>%
   left_join(df_qof_region) %>%
   group_by(year,icb_ods_code  ) %>%
   summarise(register=sum(register,na.omit=T),
      icb_list_size = sum(practice_list_size,na.omit=T),
      region_name=last(region_name),
      icb_ods_code  = last(icb_ods_code ),
      icb_name = last(icb_name)) %>%
   inner_join(df_qof_region_clean, by=join_by(icb_ods_code)) %>%
   mutate(month =as.POSIXct(paste0(substr(year, 1,4),"-01-01") ),
   icb_name = icb_name.y)


df_qof_orl_tirz <- df_orlistat_icb_month %>%
  filter(strength=="120mg") %>%
  left_join(df_tirzepatide_practice_month, by =join_by(month,region,stp,total_list_size)) %>%
  reframe(
    month,
    items_orlistat=items.x,
    items_tirzepatide=items.y,
    total_list_size,
    stp,
    regional_team,
    region) %>%
  filter(month>=as.Date("2024-01-01")) %>%
  inner_join(df_qof_ob_icb_wide %>% filter(month==as.POSIXct("2024-01-01")) %>% select(-month), by = join_by(stp==icb_ods_code )) %>%
  reframe(
    month,
    items_orlistat,
    items_tirzepatide,
    register,
    total_list_size,
    icb_list_size,
    stp,
    icb_name,
    regional_team,
    region,
    perregister_orlistat=items_orlistat / register,
    perregister_tirzepatide = items_tirzepatide / register)


df_qof_orl_tirz_long <- df_qof_orl_tirz %>%
  pivot_longer(starts_with("perregister_"),
    names_to = "drug",
    names_prefix = "perregister_",
    values_to = "per_register")

# check obesity per list size 
df_qof_orl_tirz_long <- df_qof_orl_tirz_long %>%
  mutate(obsperlist = register/total_list_size,
         perreg1000 = per_register *1000 )  

range(df_qof_orl_tirz_long$obsperlist)
```


```{r}
#| label: qof-rates-ranges
#| include: false

max_qof_orlistat<- df_qof_orl_tirz %>%
  filter(month == as.Date("2025-12-01")) %>%
  slice_max(perregister_orlistat,n=1) %>%
  select(perregister_orlistat,stp,icb_name,region )

min_qof_orlistat<- df_qof_orl_tirz %>%
  filter(month == as.Date("2025-12-01")) %>%
  slice_min(perregister_orlistat,n=1) %>%
  select(perregister_orlistat,stp,icb_name,region )


max_qof_tirzepatide<- df_qof_orl_tirz %>%
  filter(month == as.Date("2025-12-01")) %>%
  slice_max(perregister_tirzepatide,n=1) %>%
  select(perregister_tirzepatide,stp,icb_name,region )

min_qof_tirzepatide<- df_qof_orl_tirz %>%
  filter(month == as.Date("2025-12-01")) %>%
  slice_min(perregister_tirzepatide,n=1) %>%
  select(perregister_tirzepatide,stp,icb_name,region )


max_y_qof_tirzepatide<- df_qof_orl_tirz %>%
  slice_max(perregister_tirzepatide,n=1) %>%
  select(perregister_tirzepatide) %>%
  pull()


```



```{r}
#| label: plot-orlistat-tirzepatide-obesity-prevalence
#| include: false


plot_qof_orlistat <- df_qof_orl_tirz %>%
      ggplot(aes(x = month, y = perregister_orlistat)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat and tirzepatide items per QOF obesity register size: {region_name}")) +
            xlab("") +
            ylab("Rate per QOF obesity register size") 
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "QOF",
    "qof_orlistat.png"),
  plot_qof_orlistat,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

plot_qof_tirzepatide <- df_qof_orl_tirz %>%
      ggplot(aes(x = month, y = perregister_tirzepatide)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat and tirzepatide items per QOF obesity register size: {region_name}")) +
            xlab("") +
            ylab("Rate per QOF obesity register size")
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "QOF",
    "qof_tirzepatide.png"),
  plot_qof_tirzepatide,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

plot_qof_orlistat_tirzep <- df_qof_orl_tirz_long %>%
      ggplot(aes(x = month, y = per_register, colour=drug)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat and tirzepatide items per QOF obesity register size")) +
            xlab("") +
            ylab("Rate per QOF obesity register size")
          
ggsave(
  filename = here::here(
    "output",
    "icb",
    "QOF",
    "qof_combined_orlistat_tirzepatide.png"),
  plot_qof_orlistat_tirzep,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

for (region_name in regions){
  plot_qof_orlistat_tirzep_region <- df_qof_orl_tirz_long %>%
    filter(region==region_name) %>%
      ggplot(aes(x = month, y = per_register, colour=drug)) +
      facet_wrap(vars(icb_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))  +
            ggtitle(glue("Orlistat and tirzepatide items per QOF obesity register size: {region_name}")) +
            xlab("") +
            ylab("Rate per QOF obesity register size")

}





###  region patchwork
for (region_name in regions){

assign(glue("plot_qof_orlistat_tirzep_region_{region_name}"), df_qof_orl_tirz_long %>%
  filter(region == region_name) %>%
   mutate(icb_name = factor(icb_name, levels = c(levels(as.factor(icb_name)),""," ","  ","    ","     ")[1:(ceiling(length(c(levels(as.factor(icb_name))))/6)*6)])) %>%
      ggplot(aes(x = month, y = per_register, colour = drug)) +
      facet_wrap(vars(icb_name),ncol=6,nrow=2, drop = FALSE) +
        geom_line() +
          scale_y_continuous(labels = label_comma(),limits =c(0,max_y_qof_tirzepatide)) +
            theme(axis.text.x = element_text(angle =90)) +
            ggtitle(glue("Orlistat and tirzepatide items per QOF obesity register size: {region_name}")) +
            xlab("") +
            ylab("Rate per QOF obesity register size")  +
  theme_minimal())
          
}

 plot_qof_orlistat_tirzep_region_patchwork <- wrap_plots(
  `plot_qof_orlistat_tirzep_region_East of England`,
  `plot_qof_orlistat_tirzep_region_London`,
  `plot_qof_orlistat_tirzep_region_Midlands`,
  `plot_qof_orlistat_tirzep_region_North East and Yorkshire`,
  `plot_qof_orlistat_tirzep_region_North West`,
  `plot_qof_orlistat_tirzep_region_South East`,
  `plot_qof_orlistat_tirzep_region_South West`,
  ncol=1, heights = c(1,1,2,1,1,1,2))

  
ggsave(
  filename = here::here(
    "output",
    "icb",
    "QOF",
    glue("qof_combined_orlistat_tirzepatide_icb_patchwork.png")),
  plot_qof_orlistat_tirzep_region_patchwork,
  dpi = 800,
  width = 60,
  height = 60,
  units = "cm"
)




### colourful panels
df_qof_orl_tirz_long <- df_qof_orl_tirz_long %>%
  inner_join(df_regions)

plots_qof_ob_icb_split <- df_qof_orl_tirz_long %>%
  ungroup() %>%
  arrange(region) %>%
  mutate( icb_name = gsub("Integrated Care Board","ICB",icb_name),
          icb_name = glue("{str_wrap(icb_name,width=30)}"),
          icb_name = factor(icb_name,levels = unique(icb_name))) %>%
  split(.$icb_name) %>%
  purrr::map(function(data_seg) {
  ggplot(data_seg,aes(x = month, y = perreg1000,color=drug)) +
  geom_line() +
  scale_y_continuous(limits=c(0,max(df_qof_orl_tirz_long$perreg1000,na.rm = TRUE)+0.001)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle =90)) +
  xlab("") +
  ylab("Rate per 1000 QOF obesity register") +
  theme(plot.background = element_rect(fill = data_seg$col_fill),
  plot.title = element_text(size =8)) +
    ggtitle(data_seg$icb_name) +
  geom_vline(xintercept=as.POSIXct(date_tirzepatide_diab), linetype="dashed") +
  geom_vline( xintercept=as.POSIXct(date_tirzepatide_ng ), linetype="dotted") 
  })


#### legends
legend <- cowplot::get_legend(
  plots_qof_ob_icb_split[[1]] +  
    theme(
      legend.position = "bottom",
      legend.key.size = unit(0.4, "lines"), 
      legend.spacing.y = unit(0.2, "cm")    
    )
) 

legend_region <- cowplot::get_legend(
ggplot(
df_qof_orl_tirz_long %>% 
mutate(region = case_when(region =="North East and Yorkshire" ~ "North East and Yorkshire", .default = region)), 
aes(x = per_register, y = icb_name)) +
geom_tile(aes(fill = region)) +
scale_fill_manual(values = c(
"London"            =       "#8dabd371",
"South East"        =      "#e7b6e1",
"South West"        =      "#ffffb3",
"Midlands"          =      "#eeb35a38",
"North East and Yorkshire" = "#8aebe693",
"East of England"        =  "#b6e59b8c",  
"North West"             =  "#f344444d"
))+ 
theme(
legend.byrow=TRUE,
legend.position = "bottom",
legend.key.size = unit(0.4, "lines"), 
legend.spacing.y = unit(0.2, "cm")  
)
)




plot_orlistat_tirzepatide_region_split <- wrap_plots(c(plots_qof_ob_icb_split,list(legend),list(plot_spacer()),list(plot_spacer()),list(legend_region)),ncol=6,axes="collect",guides ="collect", heights=c(1,1,1,1,1,1,1,0.5)) & 
theme(legend.position = "none")

ggsave(
  filename = here::here(
  "output",
  "icb",
  "QOF",
  glue("QOF_combined_orlistat_tirzepatide_icb_split.png")),
  plot_orlistat_tirzepatide_region_split,
dpi = 800,
width = 30,
height = 30,
units = "cm"
)




```


Tirzepatide practice variation

```{r}
#| label: tirzepatide-practice-variation
#| include: false

region_wrap_n <- 12

df_tirzepatide_practice_var_month <- df_tirzepatide_practice %>%
  left_join(
    df_normalised_prescribing %>% select(practice, stp, month),
    by = join_by(practice, month)
  ) %>%
  left_join(df_regions) %>%
  group_by(month, practice) %>%
  summarise(
    items = sum(items),
    stp = last(stp),
    region = last(region),
    col_fill = last(col_fill),
    .groups = "drop"
  ) %>%
  inner_join(df_icb_stats_sicbl, by = join_by(stp == stp_id, month)) %>%
  mutate(rateper1000 = items / total_list_size * 1000) %>%
  filter(month == as.Date("2025-12-01")) %>%
  inner_join(
    df_qof_ob_icb_wide %>%
      filter(month == as.Date("2024-01-01")) %>%
      select(-month),
    by = join_by(stp == icb_ods_code)
  ) %>%
  mutate(register_factor = factor(register)) %>%
  group_by(stp) %>%
  add_count(rateper1000, name = "rate_frequency") %>%
  mutate(density = rate_frequency / sum(rate_frequency)) %>%
  select(-starts_with("icb_name"))  %>%
  ungroup() %>%
  inner_join(df_qof_icbs, by = join_by(stp == icb_ods_code)) %>%
  mutate(icb_name = glue("{str_wrap(icb_name,width=20)}\n({label_number_n(register)})"),
  stp_register = glue("{stp}\n({label_number_n(register)})"),
  region_wrap=str_wrap(region,width=region_wrap_n)) %>%
  arrange(register) %>%
  mutate(stp=factor(stp,levels = unique(stp)))
                                                                                                         
density_icb_plots <- df_tirzepatide_practice_var_month %>%
  split(.$stp) %>%
  purrr::map(function(data_seg) {

    ggplot(data_seg, aes(x = rateper1000, y = icb_name)) +
      geom_tile(aes(fill = density)) + 
      scale_fill_gradient( 
        low = "white", 
        high = "black", 
        limits = c(0, 0.0405), 
        breaks = c(0, 0.02, 0.0405) ) +
      geom_segment(
        data = data_seg,
        aes(
          x = rateper1000,
          xend = rateper1000,
          y = 0.5,
          yend = 0.8
        ),
        colour = "darkblue",
        inherit.aes = FALSE
      ) +
      scale_x_continuous(
        limits = c(0, max(df_tirzepatide_practice_var_month$rateper1000) + 0.001)
      ) +
      coord_flip() +
      labs(x = "Rate of tirzepatide prescribing per 1,000 list size", y = "") +
      theme_classic() +
      theme(plot.background = element_rect(fill = data_seg$col_fill))
  })

legend <- cowplot::get_legend(
  density_icb_plots[[1]] +  
    theme(
      legend.position = "right",
      legend.key.size = unit(0.4, "lines"), 
      legend.text = element_text(size = 7),   
      legend.title = element_text(size = 8), 
      legend.spacing.y = unit(0.2, "cm")     
    )
) 



region_cols <- df_regions %>%
  select(region, col_fill) %>%
  deframe()


legend_region <- cowplot::get_legend(
  ggplot(
    df_tirzepatide_practice_var_month %>% 
      mutate(region = case_when(region =="North East and Yorkshire" ~ "North East and Yorkshire", .default = region)), 
        aes(x = rateper1000, y = icb_name)) +
    geom_tile(aes(fill = region)) +
    scale_fill_manual(values = region_cols )+ 
    theme(
      legend.position = "right",
      legend.key.size = unit(0.4, "lines"), 
      legend.text = element_text(size = 7),   
      legend.title = element_text(size = 8), 
      legend.spacing.y = unit(0.2, "cm")  
    )
  )
     

density_plot <- wrap_plots(
  c(density_icb_plots,
  list(legend),
  list(legend_region)),
  nrow = 4,
  axes = "collect",
) &
      theme(legend.position = "none")


ggsave(
  filename = here::here(
    "output",
    "icb",
    "QOF",
    "density_icb_patchwork.png"
  ),
  density_plot,
  dpi = 800,
  width = 38,
  height = 17,
  units = "cm"
)



######## no ICB names


region_cols <- df_regions %>%
  mutate(region= str_wrap(region, width= region_wrap_n)) %>%
  select(region, col_fill) %>%
  deframe()


density_icb_plots_nonames <- df_tirzepatide_practice_var_month %>%
  split(.$stp) %>%
  purrr::map(function(data_seg) {

    ggplot(data_seg, aes(x = rateper1000, y = stp_register)) +
      geom_tile(aes(fill = density)) + 
      scale_fill_gradient( 
        low = "white", 
        high = "black", 
        limits = c(0, 0.0405), 
        breaks = c(0, 0.02, 0.0405) ) +
      geom_segment(
        data = data_seg,
        aes(
          x = rateper1000,
          xend = rateper1000,
          y = 0.5,
          yend = 0.8
        ),
        colour = "darkblue",
        inherit.aes = FALSE
      ) +
      scale_x_continuous(
        limits = c(0, max(df_tirzepatide_practice_var_month$rateper1000) + 0.001)
      ) +
      coord_flip() +
      labs(x = "Rate of tirzepatide prescribing per 1,000 list size", y = "") +
      theme_classic() +
      theme(plot.background = element_rect(fill = data_seg$col_fill))
  })


legend_region_wrap <- cowplot::get_legend(
  ggplot(
    df_tirzepatide_practice_var_month , 
        aes(x = rateper1000, y = icb_name)) +
    geom_tile(aes(fill = region_wrap)) +
    scale_fill_manual(values = region_cols ) + 
    theme(
      legend.position = "right",
      legend.key.size = unit(0.4, "lines"), 
      legend.text = element_text(size = 7),   
      legend.title = element_text(size = 8), 
      legend.spacing.y = unit(0.2, "cm")  
    )
  )




density_plot_no_names <- wrap_plots(
  c(density_icb_plots_nonames,
  list(legend),
  list(legend_region_wrap)),
  nrow = 4,
  axes = "collect",
) &
      theme(legend.position = "none")


ggsave(
  filename = here::here(
    "output",
    "icb",
    "QOF",
    "density_icb_patchwork_no_names.png"
  ),
  density_plot_no_names,
  dpi = 800,
  width = 20,
  height = 12,
  units = "cm"
)


```

```{r}

```