---
title: "Obesity and GLP-1s"
format: 
  html:
    fontsize: 11px
    mainfont: "Arial"
---

```{r}
#| label: load-packages
#| include: false

library(dplyr)
library(readr)
library(here)
library(glue)
library(tidyr)
library(stringr)
library(scales) ## format label_number
library(gt) ## gt table
library(ggplot2)
library(fpp2) # Forecasting: Principles and Practice" (2nd Edition)
library(lubridate) # interval
```

```{r}
#| label: import-data
#| include: false

directory_name <- "data"
date_tirzepatide_ng <-as.Date("2024-12-23")
date_tirzepatide_diab <-as.Date("2023-10-25")

label_number_n <- label_number(1, 1, big.mark=",")
label_perc_n <- label_percent(accuracy =.0001)

#### practice level orlistat data
df_orlistat_practice <- read_csv(here::here(directory_name,"orlistat_practice.csv.gz")) 

#### practice level tirzepatide data
df_tirzepatide_practice <- read_csv(here::here(directory_name,"tirzepatide_practice.csv.gz")) 

### practice statistics data
df_practice_stats <- read_csv(here::here(directory_name,"practice_info_full.csv.gz")) ### as far back as 2015

### ccgs info
df_hscic_ccgs <- read_csv(here::here(directory_name,"practice_ccgs.csv.gz")) %>%
  select("code","name","stp_id", "regional_team_id","org_type") 

### region info
df_regions <- read_csv(here::here("data","NHS_England_Names_and_Codes_in_England.csv")) %>%
  rename(regional_team = NHSER24CDH ,region = NHSER24NM) %>%
  dplyr::select(regional_team,region)

### QOF Obesity prevalence
df_qof_ob <-  read_csv(here::here("data", "qof", "prevalence.csv"))

### QOF regions
df_qof_region <-  read_csv(here::here("data", "qof", "geography.csv"))

```

```{r}
#| label: create-regional-stats
#| include: false

### join region information to the practice stats
df_region_stats <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  left_join(df_regions,by=join_by(regional_team_id ==regional_team )) %>%
  group_by(regional_team_id,month) %>%
  summarise(total_list_size=sum(total_list_size, na.rm = TRUE),
            regional_team_id = last(regional_team_id ),
              region = last(region ))

```

For historic reasons Integrated Care Boards (ICBs) are labelled as stp_id [Sustainability and Transformation Partnerships (STPs)]. There are multiple ways of identifying ICBs (see https://docs.google.com/document/d/1ZpfwiU_UnNX4T7y-lGPD-8i6rof69O8i-aX6xNy4li8/edit?tab=t.0)

```{r}
#| label: create-icb-stats
#| include: false

### join icb information to the practice stats
df_icb_stats <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  group_by(stp_id,month) %>%
  summarise(total_list_size=sum(total_list_size, na.rm = TRUE))

```

Quite a few practices in practice stats are missing STP info. How many are after the change in regions? (Y55 (Midlands and East of England) and Y57 (South of England) are now defunct)

```{r}
#| label: identify-max-NA-region-date 
#| include: false


na_date_max <- df_orlistat_practice %>%
  group_by(month,regional_team) %>%
  summarise(
            items=sum(items),
            regional_team = last(regional_team ))  %>%
  ungroup() %>%
  inner_join(df_region_stats,by=join_by(regional_team ==regional_team_id,month)) %>%
  mutate(rateper1000= items/total_list_size*1000) %>%
  filter(is.na(region)) %>%
  slice_max(month) %>%
  select(month) %>%
  pull()
# 2017-08-01
```


```{r}
#| label: identify-practice-stats-missing-stp
#| include: false

df_icb_stats_missing_stp <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  filter(month>na_date_max)  %>%
  filter(is.na(stp_id))

nrow(df_icb_stats_missing_stp)
# 134396

## joining on sicbl instead of pct_id
df_icb_stats_missing_stp_sicbl <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(sicbl ==code)) %>%
  filter(month>na_date_max)  %>%
  filter(is.na(stp_id))

nrow(df_icb_stats_missing_stp_sicbl)
# 2855
```

```{r}
#| label: create-icb-stats-from-sicbl
#| include: false

## remove NAs
df_icb_stats_sicbl <- df_practice_stats %>%
  left_join(df_hscic_ccgs,by=join_by(pct_id ==code)) %>%
  group_by(stp_id,month) %>%
  summarise(total_list_size=sum(total_list_size, na.rm = TRUE)) %>%
  drop_na(stp_id)

```


https://cks.nice.org.uk/topics/obesity/prescribing-information/

Important aspects of prescribing information relevant to primary healthcare are covered in this section specifically for the drugs recommended in this CKS topic. For further information on contraindications, cautions, drug interactions, and adverse effects, see the electronic Medicines Compendium (eMC) or the British National Formulary (BNF).

Orlistat
Tirzepatide


### Orlistat

NICE recommends orlistat as an option for weight management and it can be prescribed in all settings, including primary care, if people meet the criteria in table 1.

Orlistat is taken orally and may be preferable to some people who prefer not to self-inject and are willing to accept the potential adverse effects associated with this medicine.

https://cks.nice.org.uk/topics/obesity/prescribing-information/orlistat/ 

Prescribe 120 mg to be taken with each of the three main meals per day. 
It can be taken immediately before, during, or up to 1 hour after a meal.



Some orlistat prescribing practices are missing STP info. Are they before the change in region?

```{r}
#| label: missing-orlistat_stp
#| include: false


 missing_stp <- df_orlistat_practice %>%
  filter(is.na(stp))

nrow(missing_stp)
# 28775
 
 missing_stp_after_region_change <- df_orlistat_practice %>%
  filter(month>na_date_max) %>%
  filter(is.na(stp))

nrow(missing_stp_after_region_change)
# 1424

#percentage missing
nrow(missing_stp_after_region_change)  / nrow(df_orlistat_practice %>% filter(month>na_date_max)) * 100
# 0.24%


#  View(missing_stp_after_region_change)
# practices from different regions up to Feb 2020
```

Are they the same practices as practice stats?

```{r}
#| label: missing-orlistat_and_practice
#| include: false

df_orlistat_practice_with_stp <- df_orlistat_practice %>%
  filter(month>na_date_max) %>%
  drop_na(stp)
 
nrow(df_orlistat_practice_with_stp)
# 583290

df_orlistat_practice_with_stp_and_stats <- df_orlistat_practice_with_stp %>%
  inner_join(df_icb_stats_sicbl,by = join_by(stp ==stp_id,month))

nrow(df_orlistat_practice_with_stp_and_stats)
# 497925

nrow(df_orlistat_practice_with_stp) - nrow(df_orlistat_practice_with_stp_and_stats)
# 85365


### which practices have orlistat stp but no practice stats stp?
df_orlistat_practice_with_stp_no_stats <- df_orlistat_practice_with_stp %>%
  anti_join(df_orlistat_practice_with_stp_and_stats, by=join_by(stp,month))

# View(df_orlistat_practice_with_stp_no_stats)

```





```{r}
#| label: create-orlistat_strength
#| include: false


df_orlistat_practice_strength <- df_orlistat_practice%>%
  mutate(strength =  gsub("\\D", "", bnf_name))

```


```{r}
#| label: create-regional-orlistat
#| include: false

#### pct_id
df_orlistat_icb_month_pct_id <- df_orlistat_practice_strength %>%
  group_by(month,strength,stp) %>%
  summarise(
            items=sum(items),
            stp = last(stp ),
            regional_team = last(regional_team))  %>%
  ungroup()  %>%
  filter(month>na_date_max)
  
  orlistat_rows<-nrow(df_orlistat_icb_month_pct_id)
  
  df_orlistat_icb_month_pct_id <- df_orlistat_icb_month_pct_id %>%
  inner_join(df_icb_stats,by=join_by(stp ==stp_id,month)) %>%
  mutate(rateper1000= items/total_list_size*1000)

  orlistat_icb_rows<-nrow(df_orlistat_icb_month_pct_id)

  dropped_icb_months <- orlistat_rows - orlistat_icb_rows
 #1257


### sicbl
df_orlistat_icb_month_orig <- df_orlistat_practice_strength %>%
  group_by(month,strength,stp) %>%
  summarise(
            items=sum(items),
            stp = last(stp ),
            regional_team=last(regional_team))  %>%
  ungroup()  %>%
  filter(month>na_date_max)
  
  orlistat_rows<-nrow(df_orlistat_icb_month_orig)
  
  df_orlistat_icb_month <- df_orlistat_icb_month_orig %>%
  inner_join(df_icb_stats_sicbl,by=join_by(stp ==stp_id,month)) %>%
  mutate(rateper1000= items/total_list_size*1000) %>%
  drop_na(stp)

  orlistat_icb_rows<-nrow(df_orlistat_icb_month)

  dropped_icb_months <- orlistat_rows - orlistat_icb_rows
 #1300
dropped_icb_months_perc <- dropped_icb_months / orlistat_rows *100
#  15.9

 missing<- df_orlistat_icb_month_orig %>%
  anti_join(df_orlistat_icb_month, by = join_by(stp))
```



```{r}
#| label: plot-orlistat
#| include: false

plot_orlistat_icb <- df_orlistat_icb_month %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
      facet_wrap(vars(stp)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    "orlistat_icb.png"),
  plot_orlistat_icb,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

##### low strength only

plot_orlistat_icb_low <- df_orlistat_icb_month %>%
  filter(strength==60) %>%
      ggplot(aes(x = month, y = rateper1000)) +
      facet_wrap(vars(stp)) +
        geom_line(color="blue") +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    "orlistat_icb_low_strength.png"),
  plot_orlistat_icb_low,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

### by region

regions <- df_orlistat_icb_month_orig %>%
  group_by(regional_team) %>%
  summarise(regional_team=last(regional_team)) %>%
  pull()

for (region in regions){

plot_orlistat_icb_region <- df_orlistat_icb_month %>%
  filter(regional_team == region) %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
      facet_wrap(vars(stp)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    glue("orlistat_icb_{region}.png")),
  plot_orlistat_icb_region,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

}

```

### Tirzepatide TODO

```{r}
#| label: tirzepatide-strength
#| include: false


df_tirzepatide_practice_strength <- df_tirzepatide_practice %>%
  mutate(strength = gsub("[^0-9/.]", "", bnf_name),
  strength = gsub("2.4", "", strength),
  strength = gsub("/", " / ", strength))


```


```{r}
#| label: create-regional-tirzepatide
#| include: false


df_tirzepatide_practice_strength_month <- df_tirzepatide_practice_strength %>%
  group_by(month,strength,regional_team) %>%
  summarise(
            items=sum(items),
            regional_team = last(regional_team ))  %>%
  ungroup() %>%
  inner_join(df_region_stats,by=join_by(regional_team ==regional_team_id,month)) %>%
  mutate(rateper1000= items/total_list_size*1000)



df_tirzepatide_practice_month <- df_tirzepatide_practice %>%
  group_by(month,regional_team) %>%
  summarise(
            items=sum(items),
            regional_team = last(regional_team ))  %>%
  ungroup() %>%
  inner_join(df_region_stats,by=join_by(regional_team ==regional_team_id,month)) %>%
  mutate(rateper1000= items/total_list_size*1000)



```


```{r}
#| label: plot-tirzepatide
#| include: false

df<-tibble(df_tirzepatide_practice_strength_month %>% select(region)) %>%
  mutate(date_dm = as.POSIXct(date_tirzepatide_diab),  date_ng = as.POSIXct(date_tirzepatide_ng ))


plot_tirzepatide_region_strengths <- df_tirzepatide_practice_strength_month %>%
      ggplot(aes(x = month, y = rateper1000,color=strength)) +
    geom_vline(xintercept=as.POSIXct(date_tirzepatide_diab), linetype="dashed") +
    geom_vline( xintercept=as.POSIXct(date_tirzepatide_ng ), linetype="dotted") +
      facet_wrap(vars(region)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) 

          
ggsave(
  filename = here::here(
    "output",
    "tirzepatide_region_strengths.png"),
  plot_tirzepatide_region_strengths,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)

##### all tirzepatide

plot_tirzepatide_region <- df_tirzepatide_practice_month %>%
      ggplot(aes(x = month, y = rateper1000)) +
    geom_vline(xintercept=as.POSIXct(date_tirzepatide_diab), linetype="dashed") +
    geom_vline( xintercept=as.POSIXct(date_tirzepatide_ng ), linetype="dotted") +
      facet_wrap(vars(region)) +
        geom_line(color="blue") +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90)) 

          
ggsave(
  filename = here::here(
    "output",
    "tirzepatide_region.png"),
  plot_tirzepatide_region,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)


```


```{r}
#| label: combine-orlistat-tirzepatide
#| include: false

df_orlistat_practice_month_120 <- df_orlistat_practice_month %>%
  filter(strength == 120) %>%
  reframe(month,region,rateper1000_orlistat=rateper1000)


df_orlistat_tirzepatide <- df_orlistat_practice_month_120 %>%
  left_join(df_tirzepatide_practice_month %>% 
      reframe(month,region,rateper1000_tirzepatide=rateper1000), by = join_by(month,region)) %>%
  pivot_longer(cols = starts_with("rateper1000_"),
    names_to = "drug",
    names_prefix = "rateper1000_",
    values_to = "rateper1000")

```



```{r}
#| label: plot-orlistat-tirzepatide
#| include: false

plot_orlistat_tirzepatide <- df_orlistat_tirzepatide %>%
      ggplot(aes(x = month, y = rateper1000,color=drug)) +
      facet_wrap(vars(region)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    "orlistat_tirzepatide_region.png"),
  plot_orlistat_tirzepatide,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)


```

#### QOF obesity prevalence

```{r}
#| label: obesity-prevalence
#| include: false

#### clean region
df_qof_region_clean <- df_qof_region %>% 
  inner_join( df_region_stats %>% filter(month=="2024-01-01") %>% drop_na %>% select(region),
  by = join_by(region_name==region)) 


df_qof_ob_region <- df_qof_ob %>%
   left_join(df_qof_region_clean) %>%
   group_by(year,region_ods_code ) %>%
   summarise(register=sum(register),
   practice_list_size = sum(practice_list_size),
   region_name=last(region_name)) %>%
    mutate(month =as.POSIXct(paste0(substr(year, 1,4),"-01-01") )) %>%
    drop_na



```



```{r}
#| label: plot-obesity-prevalence
#| include: false

plot_qof_ob_region <- df_qof_ob_region %>%
      ggplot(aes(x = month, y = register)) +
      facet_wrap(vars(region_name)) +
        geom_line() +
          scale_y_continuous(labels = label_comma()) +
            theme(axis.text.x = element_text(angle =90))
          
ggsave(
  filename = here::here(
    "output",
    "qof_obesity_region.png"),
  plot_qof_ob_region,
  dpi = 800,
  width = 60,
  height = 30,
  units = "cm"
)



```